\section{Small modifications of predator-prey game} \label{sec:features}
There are several ways in which the classical predator-prey game can be modified to better reflect the complexities of real-world ecosystems. Some common modifications include:

1. Adding multiple prey species: In many ecosystems, predators consume multiple prey species, and the interactions between these species can have important consequences for population dynamics. To reflect this, the predator-prey game can be extended to include multiple prey species, each with its own growth and death rates, and the predator's payoffs can depend on the populations of all the prey species.

2. Incorporating resource competition: In many ecosystems, prey species compete for limited resources, and this competition can affect both their growth and death rates. To incorporate this competition, the prey-prey interaction can be modeled as a separate game, and the payoffs to the prey species can depend on the populations of other prey species.

3. Allowing for adaptive behavior: In real-world ecosystems, the populations of both predators and prey can evolve, leading to changes in their behavior and interactions. To reflect this, the predator-prey game can be extended to allow for evolutionary dynamics, where the populations of both species can evolve to better adapt to their environment.

4. Incorporating habitat destruction: Human activities, such as deforestation and urbanization, can significantly alter the habitats of both predators and prey, and this can affect their population dynamics. To reflect this, the predator-prey game can be extended to include a third player, representing the habitat, and the payoffs to the predator and prey can depend on the state of the habitat.

These modifications can provide a more accurate representation of real-world ecosystems, and help to shed light on the complex interactions between predators, prey, and their environment. However, they also introduce additional complexities and can make the analysis of the predator-prey game more challenging.
